Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-10 paper_jasa.tex
minimum p-value summary for all screening criteria
minimum p-value summary table modified
lowest p-value discussion

\begin{table}[hbtp]
\caption{Number of lineups for which most people pick the plot with minimum $p$-value. The data used is from screening criteria 1. \blue{Is this table useful? I can do the same for all the screening criteria.}} 
\begin{center}
\begin{tabular}{rrr}
  \hline
  Experiment & Total lineups & most  pick minimum $p$-value\\ 
  \hline
1 &   60 &  37 \\ 
  2 &   70 &  60 \\ 
   \hline
\end{tabular}
\end{center}
\end{table}

>>>>

Number of lineups for which most of the subjects picked the data plot based on the minimum $p$-values are shown in table \ref{tbl:pval_assumption} for both experiment 1 and 2. The $p$-values of lineups which were not chosen based on minimum $p$-value are also very small (close to minimum) as we see in both figures \ref{fig:P-val_log} and \ref{fig:P-val_log2}. We see the same pattern in figure \ref{fig:P-val_rank} where the median number of people who pick the data plot with minimum $p$-value (rank 1) are much higher than other ranks.

%\begin{table}[hbtp]
%\caption{Number of lineups for which most people pick the plot with minimum $p$-value. The data used is from screening criteria 1. } 
%\begin{center}
%\begin{tabular}{cccc}
%  \hline
%screening & Experiment & Total &  minimum $p$-value\\ 
%criteria & & lineups & picked by the most \\
%  \hline
%   & 1 &  60 &  37 \\ [-1ex]
%    \raisebox{1.5ex}{1} & 2 &  70 &  60 \\ 
%\hline
%     & 1 &  60 &  38 \\  [-1ex]
%    \raisebox{1.5ex}{2} & 2 &  70 &  61 \\ 
%\hline
%     & 1 &  60 &  38 \\  [-1ex]
%   \raisebox{1.5ex} {3} & 2 &  70 &  60 \\ 
%\hline
%     & 1 &  60 &  41 \\  [-1ex]
%    \raisebox{1.5ex}{4} & 2 &  70 &  60 \\ 
%\hline
%     & 1 &  60 &  39 \\  [-1ex]
%    \raisebox{1.5ex}{5} & 2 &  70 &  60 \\ 
%\hline
%     & 1 &  60 &  40 \\  [-1ex]
%    \raisebox{1.5ex}{6} & 2 &  70 &  60 \\ 
%   \hline
%\end{tabular}
%\end{center}
%\end{table}

\begin{table}[hbtp]
\caption{Number of lineups for which most people pick the plot with minimum $p$-value.  } 
\begin{center}
\begin{tabular}{ccc}
  \hline
screening & \multicolumn{2}{c} {lineups picked by minimum $p$-value} \\
 \cline{2-3}
criteria & Experiment 1 & Experiment 2 \\ 
  \hline
1 & 37 & 60 \\ 
  2 & 38 & 61 \\ 
  3 & 38 & 60 \\ 
  4 & 41 & 60 \\ 
  5 & 39 & 60 \\ 
  6 & 40 & 60 \\ 
\hline
  Total lineups & 60 & 70 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:pval_assumption} 
\end{table}
